### 2019-08-30 Writeup/Thesis/chapters/lit_review.tex
Changes; - Re-drafted after reading over a printed version

Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob), the unique aspects of the keys can be used to identify parties. This is achieved succinctly through the use of a fingerprint. A fingerprint is a string of alphanumerical characters that are unique to each key. Therefore the fingerprint of the two respective public keys are different, and, thus can be used for identification. There are, however, issues in how a user should link a key's fingerprint to an identity. One example way to achieve this is by meeting in-person to exchange fingerprints. This paper will, however, assume that users have been through this process.

@@

\subsection{Encoding schemes}
\label{sec:encodingSchemes}
Encoding schemes are the physical method of encoding used to represent the fingerprint. The most common way to represent the fingerprint is alphanumerically with either \textbf{Hexadecimal} (a-f/0-9) or \textbf{Base32} (2-7/A-Z). These encoding schemes are the most popular due to their intuitive simplicity and lack of unique hardware requirements such as colour screens.

@@

Graphical schemes can also be used to represent a fingerprint.

@@

\textbf{OpenSSH}. OpenSSH visual host key is an ASCII based graphical scheme used in MiTM detection when connecting to SSH servers. The image is generated by movement of the marker across a grid where every 2-bits of the generated MD5 has defines the diagonal direction of movement. For example, if the first 2-bits are \verb|11| the marker will move South East. The different characters are determined by the number of times the marker is present in that index, for example, if the maker is present on a square 4 times the character will be an equals sign (\verb|=|).

@@

\subsubsection*{Soundex}
\label{sec:soundex}
One of the earliest examples of a phonetic algorithm is known as Soundex. It was initially designed for indexing names by phonetics alongside spelling mistakes due to transpositions in letters.

Soundex produces a four-digit code for each word assessed.
The first letter of the word is retained alongside the removal of all of a, e, i, o, u, y, h and w. The remaining letters are then mapped to numbers. These mappings are displayed in Figure \ref{fig:soundexMap}.

@@

\begin{table}[h!]
    \makebox[\textwidth][c]{
        \input{tables/background/fingerprint_comparison.tex}
    }%
    \caption{Overall accuracy of correct comparison for the encoding schemes assessed}
    \label{tab:results}
\end{table}

@@

\begin{table}[h!]
    \makebox[\textwidth][c]{
        \input{tables/background/fingerprint_attacker_stren.tex}
    }%
    \caption{Paper attribute comparison}
    \label{tab:attacker}
\end{table}

>>>>

Due to the assumption that the attacking party (Eve) does not have the same public-private key pair as either party (Alice or Bob), the unique aspects of the keys can be used to identify parties. This is achieved succinctly through the use of a fingerprint. A fingerprint is a string of alphanumerical characters that are unique to each key. Therefore the fingerprint of the two respective public keys are different, and, thus can be used for identification.

@@

\subsection{Encoding schemes}
\label{sec:encodingSchemes}

\subsubsection*{Text-based schemes}
Encoding schemes are the physical method of encoding used to represent the fingerprint. The most common way to represent the fingerprint is alphanumerically with either \textbf{Hexadecimal} (a-f/0-9) or \textbf{Base32} (2-7/A-Z). These encoding schemes are the most popular due to their intuitive simplicity and lack of hardware requirements.

@@

\subsubsection*{Graphical Schemes}
Graphical schemes are a potential alternative to text based schemes. They often attempt to visualise small changes in the fingerprint to assist in altering the user to minute changes. This should, therefore, be able to provide increased usability and security. This section will explain the schemes relevant in this paper.

@@

\textbf{OpenSSH}. OpenSSH visual host key is an ASCII based graphical scheme used in MiTM detection when connecting to SSH servers. The image is generated by movement of the marker across a grid. Every 2-bits of the generated MD5 hash defines the diagonal direction of movement. For example, if the first 2-bits are \verb|11| the marker will move South East. The different characters are determined by the number of times the marker is present in that index, for example, if the maker is present on a square 4 times the character will be an equals sign (\verb|=|).

@@

\subsubsection*{Soundex}
\label{sec:soundex}
One of the earliest examples of a phonetic algorithm is known as Soundex. It was initially designed for phonetically indexing names alongside detection of transposed letters in spelling mistakes.

Soundex produces a four-digit code for each word assessed.
The first letter of the word is retained alongside the removal of all of \verb|a|, \verb|e|, \verb|i|, \verb|o|, \verb|u|, \verb|y|, \verb|h| and \verb|w|. The remaining letters are then mapped to numbers. These mappings are displayed in Figure \ref{fig:soundexMap}.

@@

\begin{table}[h!]
    \centering
    \resizebox{.8\textwidth}{!}{%

        \makebox[\textwidth][c]{
            \input{tables/background/fingerprint_comparison.tex}
        }%
    }
    \caption{Overall accuracy of correct comparison for the encoding schemes assessed}
    \label{tab:results}
\end{table}

@@

\begin{table}[h!]
    \centering
    \resizebox{.8\textwidth}{!}{%
        \makebox[\textwidth][c]{
            \input{tables/background/fingerprint_attacker_stren.tex}
        }%
    }
    \caption{Paper attribute comparison}
    \label{tab:attacker}
\end{table}

### 2019-08-30 Writeup/Thesis/code/GoogleAppScript.tex
Changes; - Updated a global code style for the paper - Fixed some more supervisor issues - Small changes
Changes; - Re-drafted after reading over a printed version

\begin{adjustbox}{width=\textwidth,keepaspectratio}
  \begin{JavascriptCode}
vvar ALGOS = ["Soundex", "Metaphone", ...];
var ALGO_SIZES = [763777, 412916, ...];

@@

  // Updates the new values
  var algo_index = 0;
  var scale_index = 0;
  for (var i = 0; i < formItems.length; i++)
  {
    if (formItems[i].getType() == "SCALE")
    {
      var rnd_index = Math.floor(Math.random() * 
      ALGO_SIZES[algo_index]) + 1;

@@

      // Moves on to the next metric when a group size 
      // has been completed
      if (scale_index != 0)
      {
        if (scale_index % QUESTION_PER_ALGO == 0) {
            algo_index++;
        }
      }
    }
  }
}
  \end{JavascriptCode}
\end{adjustbox}

>>>>

\begin{adjustbox}{width=\textwidth,keepaspectratio}
  \begin{Code}[JavascriptStyle]
vvar ALGOS = ["Soundex", "Metaphone", ...];
var ALGO_SIZES = [763777, 412916, ...];

var QUESTION_PER_ALGO = 5;

@@

  var algo_index = 0;
  var scale_index = 0;
  for (var i = 0; i < formItems.length; i++)
  {
    if (formItems[i].getType() == "SCALE")
    {
      var rnd_index = Math.floor(Math.random() * 
      ALGO_SIZES[algo_index]) + 1;

@@

      // Moves on to the next metric when a group size 
      // has been completed
      if (scale_index != 0)
      {
        if (scale_index % QUESTION_PER_ALGO == 0) {
            algo_index++;
        }
      }
    }
  }
}
  \end{Code}
\end{adjustbox}
